---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# advRpckg

<!-- badges: start -->
<!-- badges: end -->

Package containing scripts and other information for the "Advanced R Scripring" class

**New [Datacamp](https://www.datacamp.com/groups/shared_links/4d01725e80c0cadfad7198b7e1327c9e2bf83b24976b2e52c029e9aace509ccf) invite link**

## Homework

incorporate functions from "./helper_scripts/mopex_functions.R" to the package, including **roxygen comments**, **function tests**, **error handling**. hint - you can fork the repo to your github

## Installation

You can install the development version of advRpckg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github(repo = "strnda/advRpckg")
```

## Example

```{r example}
library(advRpckg)

hello()

plot(hello())
```
